Ranking Stability

### 2021-08-18 output_scripts/investigate_rankings.Rmd
current updates

---
title: "Ranking Stability"
author: "Owen G. Ward"
date: '`r Sys.Date()`'
output:
  html_document:
    # toc: true
    # toc_depth: 2
    # toc_float: true
    number_sections: FALSE
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, fig.height = 5, fig.width = 7,
  warning = FALSE, cache = TRUE
)

slides_plots <- FALSE
extra_plots <- FALSE

revision_plots <- TRUE
original_plots <- FALSE
### original plots for plots which are no longer needed, 
### revision plots are what required

@@

```{r define_functions, eval=revision_plots, include=FALSE}
model1_fn <- list(alpha.fun = function(x, y, eta1, eta2, eta3) {
  return(eta1 * x * y * exp(-eta2 * abs(x - y)) / (1 +
    exp(-eta3 * (x - y))))
})

@@

# Interevents vs rankings

```{r interevents, message=FALSE}
for(current_cohort in 1:10) {
  cat(paste("Cohort ", current_cohort, "\n", sep = ""))
  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
  stan_input_lst <- prepareDataStan(current_cohort)

  pair_events <- apply(stan_input_lst$Nm, 1, sum)

  pair_matrix <- matrix(0, nrow = 12, ncol = 12)
  for(i in seq_along(pair_events)) {
    i_ind <- stan_input_lst$I_fit[i]
    j_ind <- stan_input_lst$J_fit[i]
    pair_matrix[i_ind, j_ind] <- pair_events[i]
  }
  # pair_matrix <- clean_data$N_count[expert_rank_10[[current_cohort]],
  #                                   expert_rank_10[[current_cohort]]]
  pair_matrix <- pair_matrix[expert_rank_10[[current_cohort]],
                    expert_rank_10[[current_cohort]]]
  colnames(pair_matrix) <- expert_rank_10[[current_cohort]]
  rownames(pair_matrix) <- expert_rank_10[[current_cohort]]
  print(pair_matrix)
  cat("=====\n")

}
```

<!-- # Ranking and Events -->

<!-- We first modify the priors from the C-MMHP model which leads to -->
<!-- much improved MCMC performance. -->

<!-- We want to look at the relationship between the inferred variability -->
<!-- of the ranking and the number of interactions a given animal is involved in. -->

<!-- We plot the inferred ranks arranged by decreasing number -->
<!-- of total interactions for all 4 of the comparison models, as in Fig6a. -->

<!-- ```{r plot-rank-total-interactions, eval=FALSE} -->
<!--  for(current_cohort in 1:10) { -->
<!--    clean_data <- cleanData(full_data[[cohort_names[current_cohort]]]) -->
<!--    load(paste(data_path, -->
<!--               cohort_names[current_cohort], -->
<!--               "/cohort_mmhp_stan_result_", -->
<!--               cohort_names[current_cohort], -->
<!--               ".RData", -->
<!--               sep = "" -->
<!--               )) -->
<!--    total_inter <- rowSums(clean_data$N_count) + colSums(clean_data$N_count) -->
<!--    f_ranks <- paste("f[", order(total_inter, decreasing = TRUE), -->
<!--                     "]", sep = "") -->
<!--    f_draws <- sim_cohort_mmhp %>% select(starts_with("f")) %>% -->
<!--    pivot_longer(everything()) -->
<!--    f_draws$name <- factor(f_draws$name, levels = f_ranks) -->
<!--    plot_f <- f_draws %>% -->
<!--    ggplot(aes(name, value)) + -->
<!--    geom_boxplot() + -->
<!--    labs(title = paste("Cohort ", current_cohort, sep = ""), -->
<!--         subtitle = "Ordered by total interactions") -->
<!--    print(plot_f) -->
<!--  } -->
<!-- ``` -->

<!-- ```{r all-4-models, warning=FALSE} -->
<!-- for(current_cohort in 1:10) { -->
<!--   clean_data <- cleanData(full_data[[cohort_names[current_cohort]]]) -->
<!--   load(paste(data_path, -->
<!--              cohort_names[current_cohort], -->
<!--              "/cohort_mmhp_stan_result_", -->
<!--              cohort_names[current_cohort], -->
<!--              ".RData", -->
<!--              sep = "" -->
<!--              )) -->
<!--   load(paste(data_path, cohort_names[current_cohort], -->
<!--     "/agg_rank_stan_result_", cohort_names[current_cohort], -->
<!--     ".RData", -->
<!--     sep = "" -->
<!--   )) -->
<!--   load(paste(data_path, cohort_names[current_cohort], -->
<!--     "/cohort_hp_stan_result_", cohort_names[current_cohort], -->
<!--     ".RData", -->
<!--     sep = "" -->
<!--   )) -->
<!--   load(paste(data_path, cohort_names[current_cohort], -->
<!--     "/cohort_dchp_stan_result_", cohort_names[current_cohort], -->
<!--     ".RData", -->
<!--     sep = "" -->
<!--   )) -->
<!--   total_inter <- rowSums(clean_data$N_count) + colSums(clean_data$N_count) -->

<!--   no_method <- 4 -->
<!--   plot_latent_df <- data.frame( -->
<!--     Methods = rep(1:no_method, each = 1000 * mice_number), -->
<!--     Mice = rep(rep(1:mice_number, each = 1000), no_method), -->
<!--     force = rep(0, 1000 * mice_number * no_method) -->
<!--   ) -->
<!--   ## agg -->
<!--   x_draws <- sim_agg_rank %>% select(starts_with("x")) -->
<!--   plot_latent_df$force[(1:(1000 * mice_number))] <- -->
<!--     as.vector(as.matrix(x_draws)) -->

<!--   ## M1 -->
<!--   f_draws <- sim_cohort_hp %>% select(starts_with("f")) -->
<!--   plot_latent_df$force[(1:(1000 * mice_number)) + -->
<!--                          1000 * mice_number] <- -->
<!--     as.vector(as.matrix(f_draws)) -->

<!--   ## M2 -->
<!--   f_draws <- sim_cohort_dchp %>% select(starts_with("f")) -->
<!--   plot_latent_df$force[(1:(1000 * mice_number)) + -->
<!--                          2000 * mice_number] <- -->
<!--     as.vector(as.matrix(f_draws)) -->

<!--   ## M3 -->
<!--   f_draws <- sim_cohort_mmhp %>% select(starts_with("f")) -->
<!--   plot_latent_df$force[(1:(1000 * mice_number)) + -->
<!--                          3000 * mice_number] <- -->
<!--     as.vector(as.matrix(f_draws)) -->

<!--   plot_latent_df$Mice <- factor(plot_latent_df$Mice, -->
<!--     levels = order(total_inter, decreasing = TRUE) -->
<!--   ) -->
<!--   plot_latent_df$Method <- factor(plot_latent_df$Method, -->
<!--     labels = c("AggRanking", "C-HP", "C-DCHP", "C-MMHP") -->
<!--   ) -->
<!--   plot_cols <- col_df %>% -->
<!--   filter(method %in% c( -->
<!--     "AggRank", "C-HP", -->
<!--     "C-DCHP", "C-MMHP" -->
<!--   )) %>% -->
<!--   pull(cols) -->

<!--   p1 <- ggplot(plot_latent_df, aes(x = Mice, y = force, fill = Method)) + -->
<!--     geom_boxplot(alpha = 0.7) + -->
<!--     scale_fill_manual(values = plot_cols) + -->
<!--     ggtitle("(a)") + -->
<!--     theme_bw() + -->
<!--     theme( -->
<!--       plot.title = element_text(size = 22, hjust = 0.5, face = "bold"), -->
<!--       text = element_text(size = 20), -->
<!--       axis.text.x = element_text(size = 10), -->
<!--       legend.position = "none" -->
<!--     ) + -->
<!--     facet_grid(cols = vars(Method)) + -->
<!--     xlab("Mice (ranked by total interactions)") + -->
<!--     ylab("Latent rank") + -->
<!--     labs(title = paste("Cohort ", current_cohort, sep = "")) -->
<!--   print(p1) -->
<!-- } -->

<!-- ``` -->

<!-- Similarly, here are the corresponding plots with the animals ranked by -->
<!-- I&SI score instead. -->

<!-- ```{r isi-ranks, warning=FALSE, eval=FALSE} -->
<!-- for(current_cohort in 1:10) { -->
<!--   clean_data <- cleanData(full_data[[cohort_names[current_cohort]]]) -->
<!--   load(paste(data_path, -->
<!--              cohort_names[current_cohort], -->
<!--              "/cohort_mmhp_stan_result_", -->
<!--              cohort_names[current_cohort], -->
<!--              ".RData", -->
<!--              sep = "" -->
<!--              )) -->
<!--   total_inter <- rowSums(clean_data$N_count) + colSums(clean_data$N_count) -->
<!--   f_ranks <- paste("f[", expert_rank_10[[current_cohort]], -->
<!--                    "]", sep = "") -->
<!--   f_draws <- sim_cohort_mmhp %>% select(starts_with("f")) %>% -->
<!--   pivot_longer(everything()) -->
<!--   f_draws$name <- factor(f_draws$name, levels = f_ranks) -->
<!--   plot_f <- f_draws %>% -->
<!--   ggplot(aes(name, value)) + -->
<!--   geom_boxplot() + -->
<!--   labs(title = paste("Cohort ", current_cohort, sep = ""), -->
<!--        subtitle = "Ordered by I&SI score") -->
<!--   print(plot_f) -->
<!-- } -->

<!-- ``` -->

<!-- ```{r ranked-by-isi} -->
<!-- for(current_cohort in 1:10) { -->
<!--   clean_data <- cleanData(full_data[[cohort_names[current_cohort]]]) -->
<!--   load(paste(data_path, -->
<!--              cohort_names[current_cohort], -->
<!--              "/cohort_mmhp_stan_result_", -->
<!--              cohort_names[current_cohort], -->
<!--              ".RData", -->
<!--              sep = "" -->
<!--              )) -->
<!--   load(paste(data_path, cohort_names[current_cohort], -->
<!--     "/agg_rank_stan_result_", cohort_names[current_cohort], -->
<!--     ".RData", -->
<!--     sep = "" -->
<!--   )) -->
<!--   load(paste(data_path, cohort_names[current_cohort], -->
<!--     "/cohort_hp_stan_result_", cohort_names[current_cohort], -->
<!--     ".RData", -->
<!--     sep = "" -->
<!--   )) -->
<!--   load(paste(data_path, cohort_names[current_cohort], -->
<!--     "/cohort_dchp_stan_result_", cohort_names[current_cohort], -->
<!--     ".RData", -->
<!--     sep = "" -->
<!--   )) -->
<!--   total_inter <- rowSums(clean_data$N_count) + colSums(clean_data$N_count) -->

<!--   no_method <- 4 -->
<!--   plot_latent_df <- data.frame( -->
<!--     Methods = rep(1:no_method, each = 1000 * mice_number), -->
<!--     Mice = rep(rep(1:mice_number, each = 1000), no_method), -->
<!--     force = rep(0, 1000 * mice_number * no_method) -->
<!--   ) -->
<!--   ## agg -->
<!--   x_draws <- sim_agg_rank %>% select(starts_with("x")) -->
<!--   plot_latent_df$force[(1:(1000 * mice_number))] <- -->
<!--     as.vector(as.matrix(x_draws)) -->

<!--   ## M1 -->
<!--   f_draws <- sim_cohort_hp %>% select(starts_with("f")) -->
<!--   plot_latent_df$force[(1:(1000 * mice_number)) + -->
<!--                          1000 * mice_number] <- -->
<!--     as.vector(as.matrix(f_draws)) -->

<!--   ## M2 -->
<!--   f_draws <- sim_cohort_dchp %>% select(starts_with("f")) -->
<!--   plot_latent_df$force[(1:(1000 * mice_number)) + -->
<!--                          2000 * mice_number] <- -->
<!--     as.vector(as.matrix(f_draws)) -->

<!--   ## M3 -->
<!--   f_draws <- sim_cohort_mmhp %>% select(starts_with("f")) -->
<!--   plot_latent_df$force[(1:(1000 * mice_number)) + -->
<!--                          3000 * mice_number] <- -->
<!--     as.vector(as.matrix(f_draws)) -->

<!--   plot_latent_df$Mice <- factor(plot_latent_df$Mice, -->
<!--     levels = expert_rank_10[[current_cohort]] -->
<!--   ) -->
<!--   plot_latent_df$Method <- factor(plot_latent_df$Method, -->
<!--     labels = c("AggRanking", "C-HP", "C-DCHP", "C-MMHP") -->
<!--   ) -->
<!--   plot_cols <- col_df %>% -->
<!--   filter(method %in% c( -->
<!--     "AggRank", "C-HP", -->
<!--     "C-DCHP", "C-MMHP" -->
<!--   )) %>% -->
<!--   pull(cols) -->

<!--   p1 <- ggplot(plot_latent_df, aes(x = Mice, y = force, fill = Method)) + -->
<!--     geom_boxplot(alpha = 0.7) + -->
<!--     scale_fill_manual(values = plot_cols) + -->
<!--     ggtitle("(a)") + -->
<!--     theme_bw() + -->
<!--     theme( -->
<!--       plot.title = element_text(size = 22, hjust = 0.5, face = "bold"), -->
<!--       text = element_text(size = 20), -->
<!--       axis.text.x = element_text(size = 10), -->
<!--       legend.position = "none" -->
<!--     ) + -->
<!--     facet_grid(cols = vars(Method)) + -->
<!--     xlab("Mice (ranked by I&SI)") + -->
<!--     ylab("Latent rank") + -->
<!--     labs(title = paste("Cohort ", current_cohort, sep = "")) -->
<!--   print(p1) -->
<!-- } -->

<!-- ``` -->

<!-- Cohort 3 win loss -->

<!-- ```{r c3-win-loss} -->
<!-- current_cohort <- 3 -->
<!-- clean_data <- cleanData(full_data[[cohort_names[current_cohort]]]) -->

<!-- clean_data$N_count -->

<!-- load(paste(data_path, -->
<!--              cohort_names[current_cohort], -->
<!--              "/cohort_mmhp_stan_result_", -->
<!--              cohort_names[current_cohort], -->
<!--              ".RData", -->
<!--              sep = "" -->
<!--              )) -->

<!-- gamma_draws <- sim_cohort_mmhp %>% -->
<!--   select(starts_with("gamma")) %>% -->
<!--   pivot_longer(everything()) -->

<!-- gamma_draws$name <- factor(gamma_draws$name, -->
<!--                            levels = paste("gamma[", 1:12, "]", sep = "")) -->

<!-- gamma_draws %>% -->
<!--   ggplot(aes(name, value)) + -->
<!--   geom_boxplot() -->

<!-- zeta_draws <- sim_cohort_mmhp %>% -->
<!--   select(starts_with("zeta")) %>% -->
<!--   pivot_longer(everything()) -->

<!-- zeta_draws$name <- factor(zeta_draws$name, -->
<!--                            levels = paste("zeta[", 1:12, "]", sep = "")) -->

<!-- zeta_draws %>% -->
<!--   ggplot(aes(name, value)) + -->
<!--   geom_boxplot() -->

<!-- f_draws <- sim_cohort_mmhp %>% -->
<!--   select(starts_with("f")) %>% -->
<!--   pivot_longer(everything()) %>% -->
<!--   group_by(name) %>% -->
<!--   summarise(med = median(value)) %>% -->
<!--   arrange(-med) -->

<!-- f_draws %>% pull(name) -->

<!-- cmmhp_ranks <- c(10, 12, 7, 6, 3, 8, 2, 4, 1, 9, 11, 5) -->
<!-- clean_data$N_count[cmmhp_ranks, cmmhp_ranks] -->

<!-- c3_count <- clean_data$N_count -->
<!-- names(c3_count) <- 1:12 -->
<!-- rownames(c3_count) <- 1:12 -->
<!-- colnames(c3_count) <- 1:12 -->
<!-- isi98(c3_count) -->
<!-- isi98(c3_count[cmmhp_ranks, cmmhp_ranks]) -->
<!-- ``` -->

<!-- ## Plot Omega Lambda and f draws -->

<!-- ```{r plot-omega-lambda, message=FALSE} -->
<!-- for(current_cohort in 1:10) { -->
<!--   clean_data <- cleanData(full_data[[cohort_names[current_cohort]]]) -->
<!--   load(paste(data_path, -->
<!--              cohort_names[current_cohort], -->
<!--              "/cohort_mmhp_stan_result_", -->
<!--              cohort_names[current_cohort], -->
<!--              ".RData", -->
<!--              sep = "" -->
<!--              )) -->
<!--   fit_draws <- as_draws_array(sim_cohort_mmhp) -->
<!--   plot1 <- mcmc_hist(fit_draws, pars = "w_lambda") + -->
<!--     labs(paste("Cohort ", current_cohort, sep = "")) -->
<!--   print(plot1) -->
<!-- } -->
<!-- ``` -->

<!-- # Compare rankings with/without eta_3 -->

<!-- ```{r plot-rankings-both-models-no-eta3, message=FALSE} -->
<!-- # data_path -->
<!-- other_data_path <- "../output/revisions/lapl_check/ident_check/" -->

<!-- for(current_cohort in 1:10) { -->
<!--   load(paste(data_path, -->
<!--              cohort_names[current_cohort], -->
<!--              "/cohort_mmhp_stan_result_", -->
<!--              cohort_names[current_cohort], -->
<!--              ".RData", -->
<!--              sep = "" -->
<!--              )) -->
<!--   sim1 <- sim_cohort_mmhp -->
<!--   load(paste(other_data_path, -->
<!--              cohort_names[current_cohort], -->
<!--              "/cohort_mmhp_stan_result_", -->
<!--              cohort_names[current_cohort], -->
<!--              ".RData", -->
<!--              sep = "" -->
<!--              )) -->
<!--   sim2 <- sim_cohort_mmhp -->

<!--   all_data <- sim1 %>% -->
<!--     select(starts_with("f")) %>%  -->
<!--     pivot_longer(everything()) %>%  -->
<!--     mutate(model = "with eta3") %>%  -->
<!--     bind_rows(sim2 %>% select(starts_with("f")) %>%  -->
<!--                 pivot_longer(everything()) %>%  -->
<!--                 mutate(model = "without")) -->

<!--   f_ranks <- paste("f[", expert_rank_10[[current_cohort]], -->
<!--                    "]", sep = "")  -->
<!--   all_data$name <- factor(all_data$name, levels = f_ranks) -->

<!--   all_data$model <- factor(all_data$model) -->
<!--   comp_plot <- ggplot(all_data, aes(name, value, fill = model)) + -->
<!--     geom_boxplot() + -->
<!--     labs(title = paste("Cohort ", current_cohort, sep = ""), -->
<!--          subtitle = "Removing eta3, ordered by ISI", -->
<!--          y = "Latent Rankings") -->
<!--   print(comp_plot) -->

<!--   all_data %>% group_by(name, model) %>%  -->
<!--     summarise(model_mean = mean(value),  -->
<!--               model_sd = sd(value)) -->

<!--   all_data <- sim1 %>% -->
<!--     select(starts_with("eta") | starts_with("w_lam") | starts_with("beta")) %>%  -->
<!--     pivot_longer(everything()) %>%  -->
<!--     mutate(model = "with eta1") %>%  -->
<!--     bind_rows(sim2 %>%  -->
<!--                 select(starts_with("eta") |  -->
<!--                          starts_with("w_lam") | -->
<!--                          starts_with("beta")) %>%  -->
<!--                 pivot_longer(everything()) %>%  -->
<!--                 mutate(model = "without")) -->
<!--   all_data$model <- factor(all_data$model) -->
<!--   comp_plot <- ggplot(all_data, aes(name, value, fill = model)) + -->
<!--     geom_boxplot() + -->
<!--     labs(title = paste("Cohort ", current_cohort, sep = ""), -->
<!--          subtitle = "Comparison removing eta3", y = "Eta params") + -->
<!--     theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) -->
<!--   print(comp_plot) -->
<!--   ### -->
<!--   ## same for zeta, -->
<!--   all_data <- sim1 %>% -->
<!--     select(starts_with("zeta") ) %>%  -->
<!--     pivot_longer(everything()) %>%  -->
<!--     mutate(model = "with eta1") %>%  -->
<!--     bind_rows(sim2 %>% select(starts_with("zeta")) %>%  -->
<!--                 pivot_longer(everything()) %>%  -->
<!--                 mutate(model = "without")) -->
<!--   all_data$model <- factor(all_data$model) -->
<!--   comp_plot <- ggplot(all_data, aes(name, value, fill = model)) + -->
<!--     geom_boxplot() + -->
<!--     labs(title = paste("Cohort ", current_cohort, sep = ""), -->
<!--          subtitle = "Comparison removing eta3", y = "Zeta params") + -->
<!--     theme(axis.text.x = element_blank()) + -->
<!--     facet_wrap(~name, scales = "free") -->
<!--   print(comp_plot) -->

<!--   ### -->
<!--   all_data <- sim1 %>% -->
<!--     select(starts_with("gamma")) %>%  -->
<!--     pivot_longer(everything()) %>%  -->
<!--     mutate(model = "with eta3") %>%  -->
<!--     bind_rows(sim2 %>% select(starts_with("gamma")) %>%  -->
<!--                 pivot_longer(everything()) %>%  -->
<!--                 mutate(model = "without")) -->
<!--   all_data$model <- factor(all_data$model) -->
<!--   comp_plot <- ggplot(all_data, aes(name, value, fill = model)) + -->
<!--     geom_boxplot() + -->
<!--     labs(title = paste("Cohort ", current_cohort, sep = ""), -->
<!--          subtitle = "Comparison removing eta3", y = "Out Degree") + -->
<!--     theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) -->
<!--   print(comp_plot) -->

<!-- } -->

<!-- ``` -->

<!-- # Compare rankings with/without eta_1 -->

<!-- ```{r plot-rankings-both-models-no-eta-1, message=FALSE} -->
<!-- # data_path -->
<!-- other_data_path <- "../output/revisions/lapl_check/ident_check_no_eta1/" -->

<!-- for(current_cohort in 1:10) { -->
<!--   load(paste(data_path, -->
<!--              cohort_names[current_cohort], -->
<!--              "/cohort_mmhp_stan_result_", -->
<!--              cohort_names[current_cohort], -->
<!--              ".RData", -->
<!--              sep = "" -->
<!--              )) -->
<!--   sim1 <- sim_cohort_mmhp -->
<!--   load(paste(other_data_path, -->
<!--              cohort_names[current_cohort], -->
<!--              "/cohort_mmhp_stan_result_", -->
<!--              cohort_names[current_cohort], -->
<!--              ".RData", -->
<!--              sep = "" -->
<!--              )) -->
<!--   sim2 <- sim_cohort_mmhp -->

<!--   all_data <- sim1 %>% -->
<!--     select(starts_with("f")) %>%  -->
<!--     pivot_longer(everything()) %>%  -->
<!--     mutate(model = "with eta1") %>%  -->
<!--     bind_rows(sim2 %>% select(starts_with("f")) %>%  -->
<!--                 pivot_longer(everything()) %>%  -->
<!--                 mutate(model = "without")) -->

<!--   f_ranks <- paste("f[", expert_rank_10[[current_cohort]], -->
<!--                    "]", sep = "")  -->
<!--   all_data$name <- factor(all_data$name, levels = f_ranks) -->

<!--   all_data$model <- factor(all_data$model) -->
<!--   comp_plot <- ggplot(all_data, aes(name, value, fill = model)) + -->
<!--     geom_boxplot() + -->
<!--     labs(title = paste("Cohort ", current_cohort, sep = ""), -->
<!--          subtitle = "Comparison removing eta1, ranked by ISI", -->
<!--          y = "Latent Ranks") -->
<!--   print(comp_plot) -->

>>>>

---
title: "Ranking Stability"
author: "Owen G. Ward"
date: '`r Sys.Date()`'
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: FALSE
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, fig.height = 5, fig.width = 7,
  warning = FALSE, cache = TRUE, eval_paper = FALSE
)

paper_plots <- FALSE
# extra_plots <- FALSE

@@

```{r define_functions, include=FALSE}
model1_fn <- list(alpha.fun = function(x, y, eta1, eta2, eta3) {
  return(eta1 * x * y * exp(-eta2 * abs(x - y)) / (1 +
    exp(-eta3 * (x - y))))
})

@@

# Other Paper plots

```{r fig-3b, eval=paper_plots}
current_cohort <- 5

m1_pr <- readRDS(paste(data_path, cohort_names[current_cohort],
  "/chp_pr_matrix_", cohort_names[current_cohort],
  ".RDS",
  sep = ""
))

m2_pr <- readRDS(paste(data_path, cohort_names[current_cohort],
  "/dchp_pr_matrix_", cohort_names[current_cohort],
  ".RDS",
  sep = ""
))

m3_pr <- readRDS(paste(data_path, cohort_names[current_cohort],
  "/cmmhp_pr_matrix_", cohort_names[current_cohort],
  ".RDS",
  sep = ""
))

indep_pr <- readRDS(paste(data_path, cohort_names[current_cohort],
  "/immhp_pr_matrix_", cohort_names[current_cohort],
  ".RDS",
  sep = ""
))

matrix_lst_plot <- list(
  m1_pr[
    rev(expert_rank_10[[current_cohort]]),
    expert_rank_10[[current_cohort]]
  ],
  m2_pr[
    rev(expert_rank_10[[current_cohort]]),
    expert_rank_10[[current_cohort]]
  ]
  ,
  m3_pr[
    rev(expert_rank_10[[current_cohort]]),
    expert_rank_10[[current_cohort]]
  ],
  indep_pr[
    rev(expert_rank_10[[current_cohort]]),
    expert_rank_10[[current_cohort]]
  ]
)
# cat("Cohort ",current_cohort,"\n",sep="")
myMultiMatrixPlot(
  X = matrix_lst_plot, no_matrix = 4, n_row = 2,
  xLabels = expert_rank_10[[current_cohort]],
  yLabels = rev(expert_rank_10[[current_cohort]]),
  min = -80, max = 80, axis_cex = 2, title_cex = 1.8,
  colorPalette = "RdBu", if.emp = FALSE,
  # legend.mar=c(0.5,.5,0.5,0.5),
  title_lst = list("C-HP", "C-DCHP", "C-MMHP", "I-MMHP"),
  # title_lst = list("I-MMHP"),
  col_axis = c(-80, -40, 0, 40, 80),
  fake_matrix = FALSE,
  matrix.mar = c(2.5, 2.5, 2.5, 1)
)
mtext(text = "(b)",
      side = 3,
      line = 0.5,
      outer = TRUE,
      cex = 2.5,
      font = 2)

```{r fig-7a, eval=paper_plots}
load("../output/revisions/lapl_check/prior_check/plot_N_predict_revision.RData")
current_cohort <- 5 # cohort 1 looks worse than rest

temp_plot_df <- predict_day_mae_df_lst[[current_cohort]]
temp_plot_df$method <- factor(temp_plot_df$method,
  levels = c("mmhp", "dsnl", "m1", "m2", "m3"),
  labels = c("I-MMHP", "DSNL", "C-HP", "C-DCHP", "C-MMHP")
)
temp_plot_df$day <- factor(temp_plot_df$day)
# png(paste(plot_path,"real_predict_N_one_cohort.png",sep=""),
# width=600,height=300)

plot_cols_pred <- col_df %>%
  filter(method %in% levels(temp_plot_df$method)) %>%
  arrange(factor(method, levels = c(
    "I-MMHP", "DSNL",
    "C-HP", "C-DCHP", "C-MMHP"
  ))) %>%
  pull(cols)

p3 <- temp_plot_df %>%
  rowwise() %>%
  # mutate(norm = min(norm,60)) %>%
  # rename(Method = method) %>%
  ggplot(aes(x = method, y = mae, fill = method)) +
  geom_boxplot(alpha = 0.7) +
  scale_fill_manual(values = plot_cols_pred) +
  ggtitle("(a)") +
  theme_bw() +
  theme(
    plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
    text = element_text(size = 20),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "right"
  ) +
  facet_grid(cols = vars(day)) +
  xlab("Prediction horizon (day)") +
  ylab("MAE") +
  ylim(0, 5) + # aren't infinite but >150 and <200
  NULL
p3 + labs(fill = "Method", title = "Single Cohort")

```{r fig-7b, eval=paper_plots}
load("../output/revisions/lapl_check/prior_check/plot_N_predict_revision.RData")

all_cohort_box <- all_cohort_mae_df

all_cohort_box$method <- factor(all_cohort_box$method,
  levels = c("mmhp", "dsnl", "m1", "m2", "m3"),
  labels = c(
    "I-MMHP", "DSNL",
    "C-HP", "C-DCHP",
    "C-MMHP"
  )
)
all_cohort_box$day <- factor(all_cohort_box$day)

plot_cols_pred <- col_df %>%
  filter(method %in% levels(all_cohort_box$method)) %>%
  arrange(factor(method, levels = c(
    "I-MMHP", "DSNL",
    "C-HP", "C-DCHP", "C-MMHP"
  ))) %>%
  pull(cols)

all_cohort_box %>%
  ggplot(aes(x = method, y = norm, fill = method)) +
  # facet_grid(cols = vars(day)) +
  geom_boxplot(alpha = 0.7) +
  scale_fill_manual(values = plot_cols_pred) +
  ggtitle("(a)") +
  theme_bw() +
  theme(
    plot.title = element_text(
      size = 22,
      hjust = 0.5, face = "bold"
    ),
    text = element_text(size = 20),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "right"
  ) +
  facet_grid(cols = vars(day)) +
  # guides(color=guide_legend(title="Method")) +
  xlab("Prediction horizon (day)") +
  ylab("MAE") +
  labs(fill = "Method") +
  # ylim(0, 80) +
  NULL

```{r fig-7b-pred-rank-spearman-all-cohorts, eval=paper_plots}
load("../output/revisions/lapl_check/prior_check/plot_rank_predict.RData")

all_cohort_rank_df$method <- factor(all_cohort_rank_df$method,
  levels = c("mmhp", "dsnl", "m1", "m2", "m3"),
  labels = c(
    "I-MMHP", "DSNL", "C-HP",
    "C-DCHP", "C-MMHP"
  )
)

p7 <- ggplot(
  all_cohort_rank_df,
  aes(x = method, y = spearman, fill = method)
) +
  # geom_line(size=1.2, alpha=0.8, position=position_dodge(0.2)) +
  geom_boxplot(alpha = 0.7) +
  scale_fill_manual(values = plot_cols_pred) +
  ggtitle("(b)") +
  theme_bw() +
  theme(
    plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
    text = element_text(size = 20),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "right"
  ) +
  facet_grid(cols = vars(day)) +
  xlab("Prediction horizon (day)") +
  ylab("Spearman rank corr.") +
  # coord_cartesian(ylim=c(0,1)) +
  labs(fill = "Method")

p7
```

```{r construct data for plot, results='hide',message=FALSE,cache=TRUE, eval=paper_plots}
library(PlayerRatings)

current_cohort <- 7
# 4 best so far, or 7

load(paste(data_path, cohort_names[current_cohort],
  "/predict_simulation_", cohort_names[current_cohort],
  ".RData",
  sep = ""
))
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]],
  cut_off = 1
)

df <- full_data[[cohort_names[current_cohort]]]
df <- df[df$Actor != "Start" & df$Actor != "End", ]
df1 <- expandrows(df)
df1 <- df1[order(df1$Timestamp), ] # ensure in date order
df1$event <- 1:nrow(df1)
glick.df <- df1[, c("event", "Actor", "Recipient", "score"), with = FALSE]
# need event, actor, recipient, score
gl <- my_glicko(glick.df, history = TRUE, cval = 2)

# ------------------- period
training_end <- nrow(df[df$day <= 18, ])
testing_end <- nrow(df) - 1 # 1077 #929 for cohort 5
newx <- c(training_end:testing_end)

# ----------------- set pars for plot
my_col <- c("black", "grey", "orange", "red")
col_vec <- colorRampPalette(my_col)(mice_number)
ltypes_vec <- rep(1, mice_number) # c(1,2,3,1,2,3,1,2,3,1,2,3)
history_width <- 3
sim_width <- 0.3
shade_vec <- makeTransparent(col_vec, 0.2)
less_shade_vec <- makeTransparent(col_vec, 0.7)

# ---------------- simulation mean and sd
sim_gl_array <- array(NA, dim = c(12, testing_end - training_end + 1, 1000))
for (s in 1:1000) {
  print(s)
  temp_gl <- glickoScoreSimulationWithWindowsReturnAll(
    predict.sim = m3_predict_sim[5:8, s], # 7 for c 2 and 10
    history.df = glick.df[1:training_end, ]
  )
  history_matrix <- temp_gl$history[, , 1]

  if (testing_end > ncol(temp_gl$history[, , 1])) {
    history_matrix <- cbind(
      history_matrix,
      t(matrix(rep(
        history_matrix[, ncol(history_matrix)],
        testing_end - ncol(temp_gl$history[, , 1])
      ),
      nrow = testing_end - ncol(temp_gl$history[, , 1]),
      byrow = TRUE
      ))
    )
  } else {
    # try(
    history_matrix <- history_matrix[, 1:testing_end]
    # temp_gl$history[,1:testing_end]
    # )
  }
  sim_gl_array[, , s] <- history_matrix[, training_end:testing_end]
}
```

```{r fig-10a-glicko-rating, eval=paper_plots}
par(mar = c(3, 5, 3, 1))
testing_end <- testing_end - 1
plot(1,
  type = "n", xlab = "",
  ylab = "Glicko ranking", xlim = c(0, dim(gl$history)[2]),
  ylim = c(min(gl$history[, , 1]), max(gl$history[, , 1])),
  cex.axis = 2, cex.lab = 2
)
for (m in c(1:mice_number)) {
  # history
  lines(gl$history[m, 1:training_end, 1],
    cex = 0.6, col = col_vec[m], lwd = history_width, lty = ltypes_vec[m]
  )
  lines(c(rep(NA, training_end),
          gl$history[m, (training_end + 1):testing_end, 1]),
    cex = 0.6, col = shade_vec[m], lwd = history_width, lty = ltypes_vec[m]
  )

  # simulation
  cur_end <- testing_end
  mean_vec <- apply(sim_gl_array[m, , ], 1, function(x) mean(na.omit(x)))
  sd_vec <- apply(sim_gl_array[m, , ], 1, function(x) sd(na.omit(x)))
  polygon(c(newx, rev(newx)),
          c(mean_vec - sd_vec, rev(mean_vec + sd_vec)),
          col = shade_vec[m], border = NA)
  # polygon(c(newx), c(mean_vec-sd_vec),col = shade_vec[m], border = NA)
  lines(c(rep(NA, training_end), mean_vec),
    cex = 0.6, col = col_vec[m], lwd = 1, lty = 2
  )
}

# annotate the days
for (d in c(19:21)) {
  abline(v = nrow(df[df$day <= (d - 1), ]), lty = 2, lwd = 0.4)
  text(x = nrow(df[df$day <= (d - 1), ]), y = 2600, d)
}
mtext(text = "(a)", side = 3, line = -2.3,
      outer = TRUE, cex = 2.8, at = 0.5, font = 2)
```

```{r remove some objects, include=FALSE, eval=paper_plots}
rm(m3_predict_sim)
rm(m2_predict_sim)
rm(m1_predict_sim)
rm(mmhp_predict_sim)
rm(fit_agg_rank)
rm(fit_cohort_hp)
rm(fit_cohort_dchp)
rm(fit_cohort_mmhp)

# also removing stan fits as they can cause issues in the next chunk
```
